Ancestry linkage in hybrid zones

### 2016-02-16 drafts/hybrid_zone.tex
minor changes

\paragraph{Correlations in ancestry}
To compute correlations in local ancestry
(i.e., ``ancestry disequilibrium'', as in \citet{pool,brandvainthisvolume}),
we need only follow lineages at two sites, instead of an entire region,
the model described above requires only minor modifications,
and our numerical code can be used directly.

>>>>

\paragraph{Correlations in ancestry}
To compute correlations in local ancestry
(i.e., ``ancestry disequilibrium'', as in \citet{Pool2015,Schumer2016}),
we need only follow lineages at two sites, instead of an entire region,
the model described above requires only minor modifications,
and our numerical code can be used directly.
